Assignment 3

### 2015-02-16 rmtw/a3/latex8.tex

\SubSection{Problem Statement}
The purpose of this paper is therefore (XXX probably shouldn't use therefore to refer to the prev section.) to determine whether an organisation's development paradigm should be the basis for deciding which process and design changes to adopt.

%Maybe not this bit-----------------------------------------------------------
To explore this area, we focus on process and design practices that have been introduced at Ericsson EPG.
%Maybe not this bit-----------------------------------------------------------

>>>>

\SubSection{Problem Statement}
%big problem in industry implementing change
%could a reason for this be because they're trying to fit one thing onto something different. Focus on implementation rather than what the changes are
